---
title: "Assignment Week 5"
output: html_document
---
#### Elina Azrilyan
#### Week 5 Assignment
#####24 Sep 2018

The chart above describes arrival delays for two airlines across five destinations. Your task is to:

(1) Create a .CSV file (or optionally, a MySQL database!) that includes all of the information above. You’re encouraged to use a “wide” structure similar to how the information appears above, so that you can practice tidying and transformations as described below.

I have started by creating a .csv file with the arrival delay information provided in the assignment. I uploaded my .csv file to github to read it from an online location. The data includes blanks and it is challenging to analyze it in this format. 

```{r message=FALSE}
#install.packages("tidyverse")
#install.packages("dplyr")
require(dplyr)
require(tidyr)

AirData <- read.csv(file="https://raw.githubusercontent.com/che10vek/Data-607-Assignments/master/Assignment%205%20Data.csv", header=TRUE, sep=",")
head(AirData)
```

(2) Read the information from your .CSV file into R, and use tidyr and dplyr as needed to tidy and transform your data.

Now that we have read in our data - we need to clean up and transform it to make it possible to do analysis. 

This code will get read of NAs:
```{r}
newairdata <- subset(AirData, AirData$X.1 != "") 
head(newairdata)
```

I struggled with filling the blank cells with the value from the cell above quiet a bit. I ended up finding a function on the following webpage and adopting it a bit for my data: https://stackoverflow.com/questions/10554741/fill-in-data-frame-with-values-from-rows-above 

```{r}
f4 <- function(x, blank = "") {
# Find the values
if (is.function(blank)) {
  isnotblank <- !blank(x)
  } else {
    isnotblank <- x != blank
  }
# Fill down
x[which(isnotblank)][cumsum(isnotblank)]
}

newairdata$X <- f4(newairdata$X)
head (newairdata)
```

The following step converts this "wide"" data set into "long" data.
```{r}
air_data_long <- newairdata %>% gather(City, Count, Los.Angeles:Seattle)
air_data_long
```

(3) Perform analysis to compare the arrival delays for the two airlines.

I have manipulated the data further to get the "on time" and "delayed" data into columns.

```{r}
air_data_long2 <- air_data_long %>% spread(X.1, Count)
air_data_long2
```

Let's add a column with includes percentages to give us a beter understanding of delays for each city.

```{r}
air_data_long2 <- mutate(air_data_long2,
       PercentageDelayed = round(air_data_long2$delayed/(air_data_long2$delayed + air_data_long2$'on time')*100,2)
 )
air_data_long2 <- mutate(air_data_long2,
       PercentageOnTime = round(air_data_long2$'on time'/(air_data_long2$delayed+air_data_long2$'on time')*100,2)
)
air_data_long2
```

Now let's look at the data graphically. We do a boxplot and looks at Percentage of delayed flights for both airlines. We can see that AM West has much higher percentage delayed.

```{r}
plot(air_data_long2$X, air_data_long2$PercentageDelayed)
```

We can also look at Percent on time and that shows us the same result. Alaska has a much higher percent of on time arrivals. 

```{r}
plot(air_data_long2$X, air_data_long2$PercentageOnTime)
```

(4) Your code should be in an R Markdown file, posted to rpubs.com, and should include narrative descriptions of your data cleanup work, analysis, and conclusions. Please include in your homework submission:
 The URL to the .Rmd file in your GitHub repository. and
 The URL for your rpubs.com web page.
