---
title: "Elina Azrilyan - Data 607 - Week 9"
output: 
  html_document: 
    theme: cerulean
    toc: true
    toc_depth: 3
---

Elina Azrilyan

Week 9 Assignment

Data 607 - Fall 2018

The New York Times web site provides a rich set of APIs, as described here: http://developer.nytimes.com/docs You’ll need to start by signing up for an API key.
Your task is to choose one of the New York Times APIs, construct an interface in R to read in the JSON data, and transform it to an R dataframe.

#Bestseller Books 

The following script pulls the list of 5 best seller books as of published date 1/1/2017:

```{r}
library(jsonlite)
library(kableExtra)# manipulate table styles
suppressMessages(library(tidyverse))

#Code below is adopted from the following webpage https://cran.r-project.org/web/packages/jsonlite/vignettes/json-apis.html)

API_key <- "&api-key=f361bb0197534003a98e682f6c560185"
url <- "http://api.nytimes.com/svc/books/v3/lists/overview.json?published_date=2017-01-01"
req <- fromJSON(paste0(url, API_key))
bestsellers <- req$results$list
category1 <- bestsellers[[1, "books"]]
kable(subset(category1, select = c("author", "title", "publisher", "description")))%>% kable_styling(bootstrap_options = c("striped", "condensed"))
```

#Critics picks films

The following pulls a list of 20 critics pick movies:

```{r}
API_key <- "&api-key=f361bb0197534003a98e682f6c560185"
url <- "https://api.nytimes.com/svc/movies/v2/reviews/search.json?critics-pick=Y"
req <- fromJSON(paste0(url, API_key))
topfilms <- req$results
kable(subset(topfilms, select = c("headline", "summary_short", "display_title", "critics_pick")))%>% kable_styling(bootstrap_options = c("striped", "condensed"))
```
