---
title: "Week 3 Assignment"
output: html_document
---

####Elina Azrilyan
#### Data 607
##### 09/13/2018

Problem 3. Copy the introductory example. The vector name stores the extracted names.
     
     [1] "Moe Szyslak"       "Burns, C. Montgomery" "Rev. Timothy Lovejoy"
     [4] "Ned Flanders"      "Simpson, Homer"       "Dr. Julius Hibbert"
 
```{r}
#install.packages("stringr", repos='http://cran.us.r-project.org')
library("stringr")
raw.data <- "555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev.Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr.Julius Hibbert"
name <- unlist(str_extract_all(raw.data, "[[:alpha:]., ]{2,}"))
name
```

(a) Use the tools of this chapter to rearrange the vector so that all elements conform to the standard  first_name last_name.

```{r}
# This code removes all titles and middle initials
name2 <- str_replace(name, "\\s*\\w{1,3}[.]",  "")
name2
# This code reorders first and last names if they were in the wrong format. 
#I started with the code found on the following help page: https://stackoverflow.com/questions/33826650/last-name-first-name-to-first-name-last-name
str_replace(name2, "(\\w+),\\s(\\w+)","\\2 \\1")
```

(b) Construct a logical vector indicating whether a character has a title (i.e., Rev. and Dr.).
```{r}
name

str_detect(name, "\\s*\\w{2,3}[.]")
```

(c) Construct a logical vector indicating whether a character has a second name.
```{r}
name

str_detect(name, "\\s{1}\\w{1}[.]")
```

Problem 4. Describe the types of strings that conform to the following regular expressions and construct an example that is matched by the regular expression.

(a) [0-9]+\\$

<span style="color:red">Answer:</span> It is 1 or more numbers followed by a "$". 

Examples are: 
```{r}
test<-"jfdlsae43543fjdk$slfjsdk2354325$jfdksaf45$"
unlist(str_extract_all(test, "[0-9]+\\$"))
```

(b) \\b[a-z]{1,4}\\b

<span style="color:red">Answer:</span> It will return all lower case words between 1 and 4 letters.

Examples are:
```{r}
test<-"What a lovely day it is, there is not even a rain drop. 43543rere 235"
unlist(str_extract_all(test, "\\b[a-z]{1,4}\\b"))
```

(c) .*?\\.txt$

<span style="color:red">Answer:</span> It will return experession of any length and any characters as long as it includes ".txt"" in the end. 

Example is:

```{r}
test<-"af45$ 4832$fjdsl something.txt gfdsgf54665$%&&ggfdsf.txt"
unlist(str_extract_all(test, ".*?\\.txt$"))
```

(d) \\d{2}/\\d{2}/\\d{4}

<span style="color:red">Answer:</span> This expression will return 2digits/2digits/4digits - similar to a date format.

Example is:
```{r}
test<-"af45$ 4832$fjdsl something.txt 06/30/1984 sfjdskaj 34666 44"
unlist(str_extract_all(test, "\\d{2}/\\d{2}/\\d{4}"))
```

(e) <(.+?)>.+?</\\1>

<span style="color:red">Answer:</span> This will return any character or multiple characters surrounded by < > followed by another character or any number of characters and then followed by </ and initial character.

Example:
```{r}
test<- "fdsjkflsdaj <(sfssfdsfs)>   <tada>ffffaaaa</tada>"
unlist(str_extract_all(test, "<(.+?)>.+?</\\1>"))
```

Problem 9. The following code hides a secret message. Crack it with R and regular expressions. Hint: Some of the characters are more revealing than others! The code snippet is also available in the materials at www.r-datacollection.com.

     lcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0Tanwo
     Uwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigO
     d6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5
     fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr
     
```{r}
coded.message <- "clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0TanwoUwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigOd6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr"
unlist(str_extract_all(coded.message, "[[:punct:]A-Z]"))
```

Yes... Yes, I am:)

