---
title: "DATA607 Hands on Lab"
output:
  html_document: default
  pdf_document: default
---
Elina Azrilyan

Lab 1
You should first study the data and its associated description (i.e. “data dictionary”). You should take the data, and
create an R data frame with a subset of the columns in the dataset. You should provide relevant column names.
Your deliverable is the R Markdown code to perform these transformation tasks.

Loading data from the following location into a data frame: https://archive.ics.uci.edu/ml/machine-learning-databases/bridges/
```{r}
BridgeData <- read.csv(file="https://archive.ics.uci.edu/ml/machine-learning-databases/mushroom/agaricus-lepiota.data", header=FALSE, sep=",")
head(BridgeData)
```
Adding column names according to the data dictionary
```{r}
colnames(BridgeData) <- c("IDENTIF","RIVER", "LOCATION", "ERECTED", "PURPOSE", "LENGTH", "LANES", "CLEAR-G", "T-OR-D", "MATERIAL", "SPAN", "REL-L", "TYPE")
head(BridgeData)
```
New data frame with a subset of columns
```{r}
SBridges <- data.frame(BridgeData$IDENTIF, BridgeData$PURPOSE, BridgeData$MATERIAL, BridgeData$SPAN)
head(SBridges)
```


